---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Build Status](https://travis-ci.org/wilkersj/tumgr.svg?branch=master)](https://travis-ci.org/wilkersj/tumgr)


# tumgr
 tumgr is a tool to obtain tumor growth rates from clinical trial patient data. Output includes individual and summary data for tumor growth rate estimates as well as optional plots of the observed and predicted tumor quantity over time.  Tumor growth rates can be used to compare treatment efficacy and help predict overall survival in clinical trial datasets.

# Installation
To install the CRAN version:

```{r, echo =TRUE} 
install.packages("tumgr")  
```


To install the latest developmental version on GitHub:
```{r, echo = TRUE}
#install.packages("devtools")
#devtools::install_github("wilkersj/tumgr")
```

# Usage
```{r, echo =TRUE}  

# load library
library(tumgr)

# example data  
data(sampleData)

# generate sample plots
#par(mfrow=c(2, 3))
#out <- gdrate(sampleData, 0.10, TRUE)
#par(mfrow=c(1, 1))

# generate results with plots set to off
out <- gdrate(sampleData, 0.10, FALSE)

# summary of cases
out$models

# descriptive statistics
out$sumstats
```



