---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Build Status](https://travis-ci.org/wilkersj/tumgr.svg?branch=master)](https://travis-ci.org/wilkersj/tumgr)


# tumgr
 tumgr is a tool to obtain tumor growth rates from clinical trial patient data. Output includes individual and summary data for tumor growth rate estimates as well as optional plots of the observed and predicted tumor quantity over time.  Tumor growth rates can be used to compare treatment efficacy and help predict overall survival in clinical trial datasets.

# Installation
tumgr is now available on CRAN:

```{r, echo =TRUE} 
install.packages("tumgr")  
```


# Usage
```{r, echo =TRUE}  

# load library
library(tumgr)

# example data  
data(sampleData)

# generate results with plots set to off
#par(mfrow=c(3, 2))
out <- gdrate(sampleData, 0.10, FALSE)
#par(mfrow=c(1, 1))

# summary of cases
out$models

# descriptive statistics
out$sumstats
```



